Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-17 paper.tex
add ORION and Cyclus citations

System dynamics based fuel cycle simulators generally use a collection of
stocks to represent the state of groups of like facilities commonly referred
to as "fleets".  As the simulation steps through time, the levels of stocks
(e.g. reactor fresh fuel inventory, repository waste inventories, etc.) are
adjusted according to the calculated flow values.  Simulators that model
facility fleets built on a system dynamics foundation include VISION
\cite{jacobson_verifiable_2010}, DANESS \cite{van_den_durpel_daness_2009},
DYMOND (predecessor to DANESS), and ORION among others.  In fleet-based
modeling:

@@

One of the major motivations for the development of the Cyclus fuel cycle
simulator was creating a simulation environment that is more expressive than
more traditional fuel cycle simulators.  Cyclus was designed with a
plugin-style architecture that allows different models for facility types to
be swapped in and out trivially.  As a Cyclus simulation walks through each
time step, facilities engage in a market-like dynamic resource exchange (DRE).
They broadcast requests for material and suppliers respond with bids. The DRE
then creates a network flow problem that it optimizes to resolve which
transactions actually occur.  The plugin architecture combined with the DRE
creates a powerful and flexible environment for the natural comparison of
different modeling paradigms.

>>>>

System dynamics based fuel cycle simulators generally use a collection of
stocks to represent the state of groups of like facilities commonly referred
to as "fleets".  As the simulation steps through time, the levels of stocks
(e.g. reactor fresh fuel inventory, repository waste inventories, etc.) are
adjusted according to the calculated flow values.  Simulators that model
facility fleets built on a system dynamics foundation include VISION
\cite{jacobson_verifiable_2010}, DANESS \cite{van_den_durpel_daness_2009},
DYMOND (predecessor to DANESS), and ORION \cite{gregg_orion_2012} among
others.  In fleet-based modeling:

@@

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus_2015} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plugin-style architecture that allows different models for
facility types to be swapped in and out trivially.  As a Cyclus simulation
walks through each time step, facilities engage in a market-like dynamic
resource exchange (DRE).  They broadcast requests for material and suppliers
respond with bids. The DRE then creates a network flow problem that it
optimizes to resolve which transactions actually occur.  The plugin
architecture combined with the DRE creates a powerful and flexible environment
for the natural comparison of different modeling paradigms.
